Methods for Polyphonic Music Transcription

### 2013-12-11 paper/paper.tex
Added a song table like Poliner to the paper and added dictionary figures

@@

@@

\section{Individual Effort}
\begin{description}
\item[$\bullet$ Jeremy] wrote and evaluted the SVM method in \citet{poliner2006discriminative}, the Bayesian nonparametric method in \citet{blei2010bayesian}, and the sparse non-negative matrix factorization method in \citet{abdallah2004polyphonic}. Jeremy also wrote the paper.
\item[$\bullet$ Mark] implemented the hidden Markov model in \citet{poliner2006discriminative} and the LSTM network in \citet{bock2012polyphonic}.
\item[$\bullet$ Paul] implemented the LSTM network in \citet{bock2012polyphonic}.
\end{description}

>>>>

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

\begin{figure*}[t]
\begin{center}
\subfigure[]{
\includegraphics[scale=.6]{stft-dictionary}
\label{fig:stftdict}
}
\subfigure[]{
\includegraphics[scale=.6]{cqt-dictionary}
\label{fig:cqtdict}
}
\end{center}
\caption{(a) shows the W dictionary matrix computed for the supervised NMF method. Each column represents the spectral signature of a piano note. Notice how the base frequencies follow an exponential curve. (b) shows the H piano roll matrix output from the supervised NMF method.}
\end{figure*}

@@

\section{Individual Effort}
\begin{description}
\item[$\bullet$ Jeremy] wrote and evaluted the SVM method in \citet{poliner2006discriminative}, the non-negative matrix factorization method in \citet{abdallah2004polyphonic}, the AdaBoost method in \citet{boogaart2009note}, and wrote the paper.
\item[$\bullet$ Mark] implemented the hidden Markov model and error measures in \citet{poliner2006discriminative}, evaluated the methods, and wrote the paper.
\item[$\bullet$ Paul] implemented the non-negative matrix factorization method in \citet{abdallah2004polyphonic} and wrote the paper.
\end{description}

\begin{center}
\begin{table*}[ht]
%   \caption{Table of midi songs used for testing and training the algorithms in the paper.}
\caption{MIDI songs used for testing and training the methods in the paper.}
\begin{center}
% \setlength{\tabcolsep}{4.0em}
\begin{tabular}{L{2cm} L{4cm} L{4cm}}
% \textbf{Composer} & \textbf{Training} & \textbf{Testing} \\ \hline
Composer & Training & Testing \\ \hline
Brahms & 
Sonata C major, Op. 1 (Allegro, Andante), 7 Fantasia, Op. 116 (Andante), 3 Intermezzi, Op. 117 (Andante moderato)
& 
Sonata C major, Op. 1 (Finale), 7 Fantasia, Op. 116 (Andantino teneramente), 3 Intermezzi, Op. 117 (Andante moderato)
\\

Beethoven & Sonata No. 5, Op. 10 (Prestissimo), Sonata No. 8, Op. 13 (Rondo Allegro) & Sonata No. 11, Op. 22 (Minuetto), Sonata No. 21, Op. 53 (Adagio molto) \\

Chopin & 5 Mazurkas, Op. 7 (Vivace), Etudes, Op. 10 (Allegro, Vivace), Etudes, Op. 25 (Allegro) 
& 5 Mazurkas, Op. 7 (Vivo ma non troppo), Etudes, Op. 10 (Allegro con fuoco), Etudes, Op. 25 (Lento)
\\
Debussy & Suite bergamasque (Moderato, Menuet) & Suite bergamasque (Andante, Allegretto) \\
Mozart & Sonata No. 8 (Andantino), Sonata No. 12 (Adagio)
 & Sonata No. 8 (Allegro con spirito), Sonata No. 16 (Allegro)  \\

Schubert & 
6 Moments musicaux, Op. 94 (Allegretto moderato), Fantasia C major (Presto)
& 6 Moments musicaux, Op. 94 (Allegro vivace), Fantasia C major (Allegro)
\\

% AdaBoost & 22\% & 22 \\ 
\end{tabular}
\end{center}
\end{table*}
\end{center}
